\renewcommand{\refname}{Bibliography}

\begin{thebibliography}{99}

\bibitem{memory}
Ulrich Drepper. What Every Programmer Should Know About Memory, 2007

\bibitem{computer-architecture}
Jhon L. Hennessy, David A. Patterson Computer Architecture: A Quantitative Approach, 2017

\bibitem{optimizing-java}

Benjamin J. Evans. Optimizing Java: Practical techniques for improving JVM application performance, 2018

\bibitem{java-gc}
Tene Gil. Understanding Java Garbage Collection, 2015

\bibitem{latency}
Tene Gil. How not to measure latency, 2015

\bibitem{disruptor}
Thompson Martin, et al. Disruptor: High performance alternative to bounded queues for exchanging data between concurrent threads, 2011

\bibitem{disruptor-conference}
Trisha Gee et Mike Barker, Understanding the Disruptor, a Beginner's Guide to Hardcore Concurrency

\bibitem{disruptor-padding}
Trisha Gee, Dissecting the Disruptor: Why it’s so fast (part two) – Magic cache line padding
\bibitem{systems-performance}
Brendan Gregg. Systems Performance, 2020

\bibitem{sbe}
FIX Trading Community. Simple Binary Encoding Specification, 2019

\bibitem{chronicle}
Lawrey Peter. Chronicle Software: Low Latency Microservices, 2017

\bibitem{aeron}
Documentation technique d'Aeron Messaging

\bibitem{jol}
Shipilëv Aleksey. Java Object Layout (JOL)

\bibitem{java-objects-inside-out}
Shipilëv Aleksey. Java Objects Inside Out

\bibitem{open-jdk}
Documentation. OpenJDK

\bibitem{aeron-gh}
Aeron: Efficient Reliable UDP Unicast and Multicast Messaging.

\bibitem{java-nio}
Documentation officielle de Java NIO (New I/O)

\bibitem{java-unsafe}
Documentation sun.misc.Unsafe

\bibitem{jmh}
Shipilëv Aleksey. Java Microbenchmark Harness (JMH)

\end{thebibliography}